Teaching Debugging Collaboratively---Midway Report

### 2020-05-11 paper/midway.tex
in which we waste time making charts

\documentclass[12pt]{article}
\usepackage{multicol}
\usepackage{cite}
\usepackage{listings}
\usepackage{tikz}

@@

\begin{tikzpicture} [node distance=2em, start chain=going right,]

\end{tikzpicture}

>>>>

\documentclass[12pt]{article}
\usepackage{multicol}
\usepackage{cite}
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{positioning}

@@

\begin{tikzpicture}
  [node distance = 2em, auto, every node/.style={align=left,
    rectangle, minimum size=2em, rounded corners, fill=blue!20, inner sep=1em},
  ml/.style = {fill=green!30}]

  \node (ll) 
  {\textbf{Low Level:}\\
    RR\\
    gdb
  };
  \node (ml) [ml, right =of ll]
  {\textbf{Mid Level:}\\
    RR\\
    gdb
  };
  \node (hl) [right =of ml]
  {\textbf{High Level:}\\
    Process Vis Tools\\
    Interface to RR/GDB
  };
  \draw[<->] (ll) -- (ml);
  \draw[<->] (ml) -- (hl);
\end{tikzpicture}
